### 2009-04-04 talk/icooolps2009-dotnet/intro.tex
add an XXX that I can't solve now
briefly describe TLC
started working at the intro

\section{Introduction}
The easiest way to implement a dynamic language such as Python is to write an
interpreter; however, interpreters are slow.

The alternative is to write a compiler; writing a compiler that targets a high
level virtual machine like CLI or JVM is easier than targeting a real CPU, but
it still requires a lot of work, as
IronPython\footnote{http://www.codeplex.com/IronPython},
Jython\footnote{http://www.jython.org/}
and JRuby\footnote{http://jruby.codehaus.org/} demonstrate.

@@

>>>>

\section{Introduction}
Implementing a dynamic language such as Python with a compiler rather than with an interpreter improves performances at the cost of
an increasing complexity. Furthermore, generating code for high level virtual machines like CLI or JVM enhances portability and inter-operability.

Writing a compiler that targets a high CLI or JVM is easier than targeting a real CPU, but
it still requires a lot of work, as
IronPython\footnote{http://www.codeplex.com/IronPython},
Jython\footnote{http://www.jython.org/}
and JRuby\footnote{http://jruby.codehaus.org/} demonstrate.

@@

\anto{XXX: we first say that IronPython\&co. does JIT compilation, then we say
  we are the first to do JIT layering.  This seems a bit strange, though at
  the moment I can't think of any better way to word this concept}
